---
execute:
  message: false
  echo: false
  warning: false
  error: false

---

# Test



```{r}
# Library und dfs laden
library(plotly)
library(ggplot2)
library(dplyr)
library(tidyr)
library(htmltools)
library(htmlwidgets)
library(shiny)
library(DT)
library(RColorBrewer)
library(patchwork)
library(minpack.lm)
library(zoo)
library(purrr)
library(readxl)


plotly_list <- readRDS("C:/Users/johan/OneDrive/Desktop/SpoWi/WS 22,23/Masterarbeit - Wirkungsgrad/Daten/Probanden_Energieberechnung/xlsm/plotly_list.rds")
plotly_list_tau <- readRDS("C:/Users/johan/OneDrive/Desktop/SpoWi/WS 22,23/Masterarbeit - Wirkungsgrad/Daten/Probanden_Energieberechnung/xlsm/plotly_list_tau.rds")
plotly_list_slow <- readRDS("C:/Users/johan/OneDrive/Desktop/SpoWi/WS 22,23/Masterarbeit - Wirkungsgrad/Daten/Probanden_Energieberechnung/xlsm/plotly_list_slow.rds")


```
## Test
``` {r}
library(plotly)
library(plotly)
library(ggplot2)
library(dplyr)
library(tidyr)
library(htmltools)
library(htmlwidgets)
library(shiny)
library(DT)
library(RColorBrewer)
library(patchwork)
library(minpack.lm)
library(zoo)
library(purrr)
library(readxl)

plotly_list[10]
```

plotly_list[10]

## Proband 01 

::: {.panel-tabset}
### Test 1

plotly_list[1]

### Test 2

plotly_list[2]

### Test 3

plotly_list[3]

### Test 4

plotly_list[4]

### Test 5

plotly_list[5]

### Test 6

plotly_list[6]
:::


## Proband 01 

::: {.panel-tabset}
### Test 1

![Test 1](images/01_1.svg){group="Proband 01"}

### Test 2

![Test 2](images/01_2.svg){group="Proband 01"}

### Test 3

![Test 3](images/01_3.svg){group="Proband 01"}

### Test 4

![Test 4](images/01_4.svg){group="Proband 01"}

### Test 5

![Test 5](images/01_5.svg){group="Proband 01"}

### Test 6

![Test 6](images/01_6.svg){group="Proband 01"}
:::


## Proband 06 

::: {.panel-tabset}
### Test 1

![Test 1](images/06_1.svg){group="Proband 06"}

### Test 2

![Test 2](images/06_2.svg){group="Proband 06"}

### Test 3

![Test 3](images/06_3.svg){group="Proband 06"}

### Test 4

![Test 4](images/06_4.svg){group="Proband 06"}

### Test 5

![Test 5](images/06_5.svg){group="Proband 06"}

### Test 6

![Test 6](images/06_6.svg){group="Proband 06"}
:::



## Proband 10 

::: {.panel-tabset}
### Test 1

![Test 1](images/10_1.svg){group="Proband 10"}

### Test 2

![Test 2](images/10_2.svg){group="Proband 10"}

### Test 3

![Test 3](images/10_3.svg){group="Proband 10"}

### Test 4

![Test 4](images/10_4.svg){group="Proband 10"}

### Test 5

![Test 5](images/10_5.svg){group="Proband 10"}

### Test 6

![Test 6](images/10_6.svg){group="Proband 10"}
:::



## Proband 13 

::: {.panel-tabset}
### Test 1

![Test 1](images/13_1.svg){group="Proband 13"}

### Test 2

![Test 2](images/13_2.svg){group="Proband 13"}

### Test 3

![Test 3](images/13_3.svg){group="Proband 13"}

### Test 4

![Test 4](images/13_4.svg){group="Proband 13"}

### Test 5

![Test 5](images/13_5.svg){group="Proband 13"}

### Test 6

![Test 6](images/13_6.svg){group="Proband 13"}
:::


## Proband 15 

::: {.panel-tabset}
### Test 1

![Test 1](images/15_1.svg){group="Proband 15"}

### Test 2

![Test 2](images/15_2.svg){group="Proband 15"}

### Test 3

![Test 3](images/15_3.svg){group="Proband 15"}

### Test 4

![Test 4](images/15_4.svg){group="Proband 15"}

### Test 5

![Test 5](images/15_5.svg){group="Proband 15"}

### Test 6

![Test 6](images/15_6.svg){group="Proband 15"}
:::

## Proband 19

::: {.panel-tabset}
### Test 1

![Test 1](images/19_1.svg){group="Proband 19"}

### Test 2

![Test 2](images/19_2.svg){group="Proband 19"}

### Test 3

![Test 3](images/19_3.svg){group="Proband 19"}

### Test 4

![Test 4](images/19_4.svg){group="Proband 19"}

### Test 5

![Test 5](images/19_5.svg){group="Proband 19"}

### Test 6

![Test 6](images/19_6.svg){group="Proband 19"}
:::


## Proband 20

::: {.panel-tabset}
### Test 1

![Test 1](images/20_1.svg){group="Proband 20"}

### Test 2

![Test 2](images/20_2.svg){group="Proband 20"}

### Test 3

![Test 3](images/20_3.svg){group="Proband 20"}

### Test 4

![Test 4](images/20_4.svg){group="Proband 20"}

### Test 5

![Test 5](images/20_5.svg){group="Proband 20"}

### Test 6

![Test 6](images/20_6.svg){group="Proband 20"}
:::


## Proband 22

::: {.panel-tabset}
### Test 1

![Test 1](images/22_1.svg){group="Proband 22"}

### Test 2

![Test 2](images/22_2.svg){group="Proband 22"}

### Test 3

![Test 3](images/22_3.svg){group="Proband 22"}

### Test 4

![Test 4](images/22_4.svg){group="Proband 22"}

### Test 5

![Test 5](images/22_5.svg){group="Proband 22"}

### Test 6

![Test 6](images/22_6.svg){group="Proband 22"}
:::

## Proband 23 

::: {.panel-tabset}
### Test 1

![Test 1](images/23_1.svg){group="Proband 23"}

### Test 2

![Test 2](images/23_2.svg){group="Proband 23"}

### Test 3

![Test 3](images/23_3.svg){group="Proband 23"}

### Test 4

![Test 4](images/23_4.svg){group="Proband 23"}

### Test 5

![Test 5](images/23_5.svg){group="Proband 23"}

### Test 6

![Test 6](images/23_6.svg){group="Proband 23"}
:::
