---
execute: 
  message: false
  echo: false
  warning: false
  error: false
bibliography: references.bib
lang: de
number-sections: false
editor: 
  markdown: 
    wrap: 72
---

```{css}
#| echo: false
p {
  text-align: justify
}
caption {
  text-align: justify;
}

```

```{r}
library(dplyr)
library(tidyr)
library(readxl)
library(ggplot2)
library(DT)
library(extrafont)
library(shiny)
library(plotly)
library(shinylive)
```



### Tabellen mit EPOC-Parametern aus verschiedenen Untersuchungen

#### Tabelle EPOC

+--------+--------+--------+--------+--------+--------+--------+
| Quelle | EPO    | EPO    | EPO    | EPO    | O~2~-S | EPO    |
|        | C~PCR~ | C~PCR~ | C~ges~ | C~ges~ | p      | C~NET~ |
|        | \[ml   | \[l\]  | \[ml   | \[l\]  | eicher |        |
|        | \cdot  |        | \cdot  |        |        |        |
|        | k      |        | k      |        |        |        |
|        | g      |        | g      |        |        |        |
|        | ^-1^\] |        | ^-1^\] |        |        |        |
+========+========+========+========+========+========+========+
| @Hi    |        |        |        | 7,5    |        |        |
| ll1924 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      | 36,8   | 2,50   | \-     | \-     |        |        |
| Margar |        |        |        |        |        |        |
| ia1933 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      | \-     | \-     | 75,0   | 4,65   |        |        |
| Margar |        |        |        |        |        |        |
| ia1963 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      | \-     | 2,77   | \-     | \-     |        |        |
| Margar |        |        |        |        |        |        |
| ia1964 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| \@D    | 45.0   | \-     | \-     | \-     |        |        |
| iPramp |        |        |        |        |        |        |
| e      |        |        |        |        |        |        |
| ro1971 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      | 40,00  | \-     | \-     | \-     |        |        |
| Margar |        |        |        |        |        |        |
| ia1972 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| \@Di   | 32 .0  |        |        |        |        |        |
| Prampe |        |        |        |        |        |        |
| ro1973 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      | \-     | \-     | 67,0   | 5,00   |        |        |
| Shepha |        |        |        |        |        |        |
| rd1973 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Kat   | \-     | \-     | 68,0   | 4,89   |        |        |
| ch1973 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Parn  | \-     | \-     | 74,0   | 5,02   |        |        |
| at1975 |        |        | \      |        |        |        |
|        |        |        | [\^2\] |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      | 37,45  | 2,79   | 70,0   | 4,93   |        |        |
| Robert |        |        |        |        |        |        |
| s1978a |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @      |        |        |        |        | 0,55 L |        |
| Margar |        |        |        |        |        |        |
| ia1976 |        |        |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Bene  | \-     | 1,94   | \-     | \-     |        |        |
| ke2002 |        | (0,31) |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Bene  | 32.13  | 2.48   |        |        |        |        |
| ke2004 | +-     | +-     |        |        |        |        |
|        | 2.59   | 0.20   |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Astra | 21,43  | 1.5 L  |        |        |        |        |
| nd2003 |        | (body  |        |        |        |        |
|        |        | weight |        |        |        |        |
|        |        | about  |        |        |        |        |
|        |        | 70 kg) |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Fra   | Sehr   | Für    | Sehr   | Sehr   | Für    | Sehr   |
| ncesca | l      | Muske  | l      | l      | Muske  | l      |
| to2003 | eicht: | lm     | eicht: | eicht: | lm     | eicht: |
|        | 11,8 ± | asse\~ | 27,9 ± | 0,558  | asse\~ | 0,0118 |
|        | 2,4    | ak     | 4,4    | ±      | ak     | ±      |
|        | ml/kg  | tiv\~: | ml/kg  | 0,088  | tiv\~: | 0,0024 |
|        |        | 20kg   |        | L      | 20kg   | l/kg   |
|        | L      |        | L      |        |        |        |
|        | eicht: | Sehr   | eicht: | L      | Sehr   | L      |
|        | 20,8 ± | l      | 50,6 ± | eicht: | l      | eicht: |
|        | 3,4    | eicht: | 7,6    | 1,012  | eicht: | 0,0208 |
|        | ml/kg  | 0,236  | ml/kg  | ±      | 27,9 ± | ±      |
|        |        | ±      |        | 0,152  | 4,4    | 0,0034 |
|        | Mo     | 0,048  | Mo     | L      | ml/kg  | l/kg   |
|        | derat: | L      | derat: |        |        |        |
|        | 32,9 ± |        | 85,4 ± | Mo     | L      | Mo     |
|        | 3,5    | L      | 7,8    | derat: | eicht: | derat: |
|        | ml/kg  | eicht: | ml/kg  | 1,708  | 50,6 ± | 0,0329 |
|        |        | 0,416  |        | ±      | 7,6    | ±      |
|        |        | ±      |        | 0,156  | ml/kg  | 0,0035 |
|        |        | 0,068  |        | L      |        | l/kg   |
|        |        | L      |        |        | Mo     |        |
|        |        |        |        |        | derat: |        |
|        |        | Mo     |        |        | 85,4 ± |        |
|        |        | derat: |        |        | 7,8    |        |
|        |        | 0,658  |        |        | ml/kg  |        |
|        |        | ±      |        |        |        |        |
|        |        | 0,070  |        |        |        |        |
|        |        | L      |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Duns  | 27.27  | 2,09 ± | \-     | \-     |        |        |
| t2023a | ± 8.43 | 0,64   |        |        |        |        |
|        |        | \      |        |        |        |        |
|        |        | [\^3\] |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+
| @Duns  | 28.33  | 2.538  |        |        |        |        |
| t2023b | ± 5.28 | ±      |        |        |        |        |
|        |        | 0.445  |        |        |        |        |
+--------+--------+--------+--------+--------+--------+--------+

: **Tabelle mit absoluten Werten aus verschiedenen Untersuchungen der
EPOC** (angelehnt an @Roberts1978)

+-------+-------+-------+-------+-------+-------+---------------+
|       | **A   |       | **B   |       | **C   | **W~PCR~      |
| **Que | \     | **    | \     | **    | \     | \[kJ\]**      |
| lle** | [ml** | tauA\ | [ml** | tauB\ | [ml** |               |
|       | \cdot | \[min | \cdot | \[min | \cdot |               |
|       | **mi  | \]**  | **mi  | \]**  | **min |               |
|       | n^~-1 |       | n^~-1 |       | ^~-1~ |               |
|       | ~^\]\ |       | ~^\]\ |       | ^\]** |               |
|       | **    |       | **    |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| \@Ma  |       |       |       | 12-17 |       |               |
| rgari |       |       |       | min   |       |               |
| a1933 |       |       |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @DiPr |       | *(0,  |       |       |       | ...           |
| amper |       | 42 -  |       |       |       |               |
| o1973 |       | 0     |       |       |       |               |
|       |       | ,5)*  |       |       |       |               |
|       |       |       |       |       |       |               |
|       |       | T1/2: |       |       |       |               |
|       |       |       |       |       |       |               |
|       |       | 27s   |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @Katc | ...   |       |       | 11.76 |       |               |
| h1973 |       |       |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| \@Ro  | 2     | 1,51  | 0     | \-    | \-    |               |
| berts | ,330  |       | ,372  |       |       |               |
| 1978a |       |       |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @DiPr |       |       |       |       |       | ...           |
| amper |       |       |       |       |       |               |
| o1981 |       |       |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @B    |       |       |       |       |       |               |
| arsto |       |       |       |       |       |               |
| w1991 |       |       |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @O    | \-    | M:    | \-    | VH:   | \-    |               |
| zyene |       | 0,48  |       | 7,67  |       |               |
| r2001 |       | ± 0,1 |       | ± 2   |       |               |
|       |       |       |       | ,05\  |       |               |
|       |       | H:    |       |       |       |               |
|       |       | 0,7 ± |       | S:    |       |               |
|       |       | 0,18  |       | 8,98  |       |               |
|       |       |       |       | ±     |       |               |
|       |       | VH:   |       | 6,32  |       |               |
|       |       | 0,55  |       |       |       |               |
|       |       | ±     |       |       |       |               |
|       |       | 0,08  |       |       |       |               |
|       |       |       |       |       |       |               |
|       |       | S:    |       |       |       |               |
|       |       | 0,58  |       |       |       |               |
|       |       | ±     |       |       |       |               |
|       |       | 0,18  |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @     | 2     | 0,70  | 0     | 14,10 | 0,329 | 40,2 ± 10,6   |
| Benek | ,777  | ± 0,2 | ,675  | ±     | ±     |               |
| e2002 | ± 0   |       | ± 0   | 13,50 | 0,48  |               |
|       | ,445  |       | ,257  |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| \@A   |       | ≈ 0,5 |       | ≈ 15  |       |               |
| stran |       |       |       |       |       |               |
| d2003 |       |       |       |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @     | 2,49  | 0,84  | 0,51  | 7,34  | 0,42  |               |
| Dunst | ±     | ±     | ±     | ±     | ±     |               |
| 2023a | 0,62  | 0,13  | 0,34  | 3,67  | 0,09  |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @     | 3s: 1 | 3s:   | 3s: 0 | 3s:   | 3s:   | 3s: 31,83 ±   |
| Dunst | ,985  | 0,82  | ,195  | 5,72  | 0,391 | 6,98          |
| 2023b | ± 0   | ±     | ± 0   | ±     | ± 0   |               |
|       | ,436  | 0,14  | ,167  | 2,52  | ,058  | 8s: 46,50 ±   |
|       |       |       |       |       |       | 3,79          |
|       | 8s: 2 | 8s:   | 8s: 0 | 8s:   | 8s:   |               |
|       | ,740  | 0,84  | ,418  | 6,46  | 0,391 | 12s: 51,24 ±  |
|       | ± 0   | ±     | ± 0   | ±     | ±     | 9,52          |
|       | ,381  | 0,12  | ,133  | 3,38  | 0,043 |               |
|       |       |       |       |       |       | 60s: 53,73 ±  |
|       | 12s:  | 12s:  | 12s:  | 12s:  | 12s:  | 9,96          |
|       | 2     | 0,84  | 0     | 8,03  | 0,411 |               |
|       | ,878  | ± 13  | ,577  | ±     | ±     |               |
|       | ± 0   |       | ± 0   | 3,10  | 0,058 |               |
|       | ,501  | 60s:  | ,119  |       |       |               |
|       |       | 0,85  |       | 60s:  | 60s:  |               |
|       | 60s:  | ±13   | 60s:  | 9,36  | 0,532 |               |
|       | 3     |       | 0     | ±     | ±     |               |
|       | ,032  |       | ,981  | 5,11  | 0,106 |               |
|       | ± 0   |       | ± 0   |       |       |               |
|       | ,447  |       | ,298  |       |       |               |
+-------+-------+-------+-------+-------+-------+---------------+
| @L    | \-    | \-    | \-    | \-    | \-    | 10s: 102,93 ± |
| angle |       |       |       |       |       | 25,91         |
| y2024 |       |       |       |       |       |               |
|       |       |       |       |       |       | 15s: 109,83 ± |
|       |       |       |       |       |       | 28,30         |
|       |       |       |       |       |       |               |
|       |       |       |       |       |       | 30s: 126,39 ± |
|       |       |       |       |       |       | 24,25         |
+-------+-------+-------+-------+-------+-------+---------------+
| ...   | ...   | ...   | ...   | ...   | ...   | ...           |
+-------+-------+-------+-------+-------+-------+---------------+

: Parameter Bi-Exponentialfunktion - M, moderate; H, heavy; VH, very
heavy; S, severe exercise intensities

``` r
# In diPrampero1981
#deltaHPC = 46 + 1.0 kJ • mol-1 nach (Wilkie 1968)

#deltaP is relatively unaffected by PC concentration, varying from 52 to 44 kJ/mol for a de- crease of PC from 15 to 4 mmol/kg.

#deltaH and deltaG indicate the enthalpy (free energy) change per mole advancement of the reaction

#Weitere WErte in einer Tabell und in Mahler1979

#In diPrampero1973

##Assuming also that 20-25 kg of muscle are involved in this exercise, i.e., 30-35% of the total body weight, the amount of phosphagen split per kilogram of active muscle amounts to 24-28 mmole.
```

### Tabelle körpereigene Energiespeicher

+------+------+------+------+------+------+
| Qu   | ATP  | ATP  | CrP  | U    | Nut  |
| elle | -Spe | -    | -Spe | mrec | zbar |
|      | i    | Rate | i    | h    |      |
|      | cher |      | cher | nung |      |
|      |      |      |      | s    |      |
|      |      |      |      | rate |      |
+======+======+======+======+======+======+
| \    |      |      |      | ATP: |      |
| @Loh |      |      |      | 0,09 |      |
| mann |      |      |      | cal  |      |
| 1937 |      |      |      | W    |      |
|      |      |      |      | ärme |      |
|      |      |      |      | m    |      |
|      |      |      |      | enge |      |
|      |      |      |      | in   |      |
|      |      |      |      | cal  |      |
|      |      |      |      | für  |      |
|      |      |      |      | die  |      |
|      |      |      |      | in   |      |
|      |      |      |      | e    |      |
|      |      |      |      | inem |      |
|      |      |      |      | G    |      |
|      |      |      |      | ramm |      |
|      |      |      |      | Fr   |      |
|      |      |      |      | o    |      |
|      |      |      |      | schm |      |
|      |      |      |      | u    |      |
|      |      |      |      | skel |      |
|      |      |      |      | e    |      |
|      |      |      |      | ntha |      |
|      |      |      |      | l    |      |
|      |      |      |      | tene |      |
|      |      |      |      | M    |      |
|      |      |      |      | enge |      |
|      |      |      |      | ATP  |      |
|      |      |      |      |      |      |
|      |      |      |      | CrP: |      |
|      |      |      |      | 0,23 |      |
|      |      |      |      | cal  |      |
|      |      |      |      | W    |      |
|      |      |      |      | ärme |      |
|      |      |      |      | m    |      |
|      |      |      |      | enge |      |
|      |      |      |      | in   |      |
|      |      |      |      | cal  |      |
|      |      |      |      | für  |      |
|      |      |      |      | die  |      |
|      |      |      |      | in   |      |
|      |      |      |      | e    |      |
|      |      |      |      | inem |      |
|      |      |      |      | G    |      |
|      |      |      |      | ramm |      |
|      |      |      |      | Fr   |      |
|      |      |      |      | o    |      |
|      |      |      |      | schm |      |
|      |      |      |      | u    |      |
|      |      |      |      | skel |      |
|      |      |      |      | e    |      |
|      |      |      |      | ntha |      |
|      |      |      |      | l    |      |
|      |      |      |      | tene |      |
|      |      |      |      | M    |      |
|      |      |      |      | enge |      |
|      |      |      |      | ATP  |      |
+------+------+------+------+------+------+
| @Hul | 24,3 |      | 67,8 |      |      |
| tman | ±    |      | ±    |      |      |
| 1967 | 2,1  |      | 7,0  |      |      |
+------+------+------+------+------+------+
| \@   | 6    |      | 2    |      |      |
| Keul | mmol |      | 0-30 |      |      |
| 1972 | pro  |      | mmol |      |      |
|      | kg   |      | pro  |      |      |
|      | Musk |      | kg   |      |      |
|      | e    |      | Musk |      |      |
|      | lfeu |      | e    |      |      |
|      | c    |      | lfeu |      |      |
|      | htge |      | c    |      |      |
|      | w    |      | htge |      |      |
|      | icht |      | w    |      |      |
|      |      |      | icht |      |      |
+------+------+------+------+------+------+
| @    | R    |      | R    |      |      |
| Knut | uhe: |      | uhe: |      |      |
| tgen | 4,82 |      | 17,9 |      |      |
| 1973 | ±    |      | ±    |      |      |
|      | 0    |      | 2,06 |      |      |
|      | ,349 |      | mmol |      |      |
|      |      |      | .    |      |      |
|      | B    |      | kg-1 |      |      |
|      | elas |      |      |      |      |
|      | t    |      | Nach |      |      |
|      | ung: |      | B    |      |      |
|      | 2,56 |      | elas |      |      |
|      | ±    |      | t    |      |      |
|      | 0    |      | ung: |      |      |
|      | ,662 |      | 3,56 |      |      |
|      |      |      | ±    |      |      |
|      |      |      | 0    |      |      |
|      |      |      | ,716 |      |      |
+------+------+------+------+------+------+
| @S   | 2-3  |      | 7-9  | 0    |      |
| tege | mmol |      | mmol | .9kJ |      |
| mann | /    |      | /    | / kg |      |
| 1991 | 100g |      | 100g | M    |      |
|      | Tr   |      | Tr   | u    |      |
|      | o    |      | o    | skel |      |
|      | cken |      | cken | m    |      |
|      | m    |      | m    | asse |      |
|      | asse |      | asse | a    |      |
|      |      |      |      | u    |      |
|      | 2    |      | 7    | sges |      |
|      | 0-30 |      | 0-90 | a    |      |
|      | mmol |      | mmol | mten |      |
|      | /kg  |      | /kg  | Spei |      |
|      |      |      |      | c    |      |
|      |      |      |      | hern |      |
|      |      |      |      |      |      |
|      |      |      |      | 30,5 |      |
|      |      |      |      | kJ   |      |
|      |      |      |      | pro  |      |
|      |      |      |      | Mol  |      |
|      |      |      |      | ATP  |      |
+------+------+------+------+------+------+
| @    | 24,0 |      | 76,5 | Sp   | Mi   |
| Gait | ±    |      | ±7,2 | rint | n    |
| anos | 2,7  |      |      | 1    | imum |
| 1993 |      |      |      | from | PCR  |
|      |      |      |      | PCr  | 12,2 |
|      |      |      |      | 44,3 | ±    |
|      |      |      |      | ±    | 3,7  |
|      |      |      |      | 4,7  |      |
|      |      |      |      |      |      |
|      |      |      |      | Spr  |      |
|      |      |      |      | i    |      |
|      |      |      |      | nt&: |      |
|      |      |      |      | 25,3 |      |
|      |      |      |      | ±    |      |
|      |      |      |      | 9,7  |      |
+------+------+------+------+------+------+
| @    | 5-6  |      | 25   | 30   |      |
| Weic |      |      |      | kJ   |      |
| ker1 |      |      |      | pro  |      |
| 994, |      |      |      | Mol  |      |
| 46   |      |      |      | ATP  |      |
|      |      |      |      |      |      |
|      |      |      |      | 43,1 |      |
|      |      |      |      | kJ   |      |
|      |      |      |      | pro  |      |
|      |      |      |      | Mol  |      |
|      |      |      |      | CrP  |      |
+------+------+------+------+------+------+
| @    | 5 m  | S    | PC   | the  | Mi   |
| Astr | m    | p    | con  | pote | n    |
| and2 | ol - | rint | c    | n    | umum |
| 003, | kg"  |      | entr | tial | zu   |
| 249  | in   |      | a    | t    | 2    |
|      | f    |      | tion | otal | mmol |
|      | resh |      | of   | e    | .    |
|      | m    |      | 17   | n    | kg-1 |
|      | u    |      | mmol | ergy |      |
|      | scle |      | :    | y    |      |
|      |      |      | k    | ield |      |
|      |      |      | g"!, | is   |      |
|      |      |      |      | app  |      |
|      |      |      |      | r    |      |
|      |      |      |      | oxim |      |
|      |      |      |      | a    |      |
|      |      |      |      | tely |      |
|      |      |      |      | .9   |      |
|      |      |      |      | kJ   |      |
|      |      |      |      | (.2  |      |
|      |      |      |      | k    |      |
|      |      |      |      | c    |      |
|      |      |      |      | al). |      |
+------+------+------+------+------+------+
| @    | 5    |      | 1    | 30   | Nur  |
| DeMa |      |      | 5-20 | u    | ca.  |
| rees |      |      |      | nter | 22   |
| 2003 |      |      |      | Stan | der  |
|      |      |      |      | d    | 25   |
| @    |      |      |      | artb | nu   |
| Heck |      |      |      | e    | t    |
| 2006 |      |      |      | ding | zbar |
|      |      |      |      | u    |      |
| @    |      |      |      | ngen |      |
| Heck |      |      |      |      |      |
| 2022 |      |      |      | 52   |      |
|      |      |      |      | in   |      |
|      |      |      |      | an   |      |
|      |      |      |      | d    |      |
|      |      |      |      | eren |      |
|      |      |      |      | leb  |      |
|      |      |      |      | e    |      |
|      |      |      |      | nden |      |
|      |      |      |      | Zel  |      |
|      |      |      |      | len, |      |
|      |      |      |      | .B   |      |
|      |      |      |      | in   |      |
|      |      |      |      | r    |      |
|      |      |      |      | oten |      |
|      |      |      |      | Blut |      |
|      |      |      |      | k    |      |
|      |      |      |      | örpe |      |
|      |      |      |      | r    |      |
|      |      |      |      | chen |      |
|      |      |      |      | (Ery |      |
|      |      |      |      | t    |      |
|      |      |      |      | horz |      |
|      |      |      |      | y    |      |
|      |      |      |      | ten) |      |
|      |      |      |      | (S.  |      |
|      |      |      |      | 345) |      |
+------+------+------+------+------+------+
| \    |      |      | 1    |      |      |
| @Fra |      |      | 7    |      |      |
| nces |      |      | .8 - |      |      |
| cato |      |      | 37.7 |      |      |
| 2003 |      |      |      |      |      |
+------+------+------+------+------+------+

```{r}
# Gaitanos
## ATP energy provision of 100 kJ/mol nach MCGlivery 1975
##Estimates of ATP production from anaerobic sources during first and final 6-s sprint of exercise test
##ATP Production mmol/kg dy weight
```